\documentclass[letterpaper, 11pt]{article}
\usepackage[margin=0.55in]{geometry}

\usepackage{calc}
\usepackage{anyfontsize}
\usepackage{sweet_resume}

\usepackage{enumitem}
\usepackage{tabularx}

\usepackage[T1]{fontenc}
\usepackage{setspace}
\usepackage[usenames,dvipsnames]{xcolor}

\pagenumbering{gobble}

\newcommand{\CawColorName}{Black}
\newcommand{\CawColorTitle}{RoyalBlue}
\newcommand{\CawColorHeaderA}{MidnightBlue}
\newcommand{\CawColorSubHeaderA}{MidnightBlue}
\newcommand{\CawColorSubHeaderB}{Black}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Macros %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\OriginalLetterContents}{%
\par \bigskip \bigskip \bigskip \bigskip
To CU's Hiring Manager,
\par \bigskip \bigskip
Hi, my name is Christine and I am looking to apply for the position of
video production specialist. I read your post on the CU website and am very
interested in joining your team. First let me start with a little history on
my part. I graduated from film school in 2008 with a bachelor’s degree in
film and video production. I have been working as an editor for the past
five years where I have worked on tv shows and web content.
\par \bigskip \smallskip
I moved to Colorado to be with my fiancé, as he has moved here for work.
Now, I too, am looking for a job. I understand you want to film classes
for online use, and I think my background really matches your needs.
\par \bigskip \smallskip
I do feel I have the experience and knowledge to join your team, and make
online content for students to advance their education. Not only that, I
like working in teams and with other people. I am a creative person who
likes to collaborate while making videos.
\par \bigskip \bigskip
Best regards,
\par \smallskip
Christine Waynick
}

\newcommand{\LetterContents}{%
\par \bigskip \bigskip \bigskip \bigskip
To CU's Hiring Manager,
\par \bigskip \bigskip

I'm interested in the OIT's Video Production Specialist position listed
on CU Careers. My fiancé took a tech job here in Boulder late last year,
and we spent the past few months wrapping things up and moving. Now that
we're all settled in, I'm starting to look for a job in my field as well.
\par \bigskip \smallskip

I've been working in video production/post production for several years
now, and I have direct experience creating video for streaming and
broadcast. In particular, my time spent working on reality TV gave me
first-hand knowledge of how to make high-quality video on a budget.
\par \bigskip \smallskip

I also have a fair amount of A/V background. During my college years, I
worked at my university's equipment checkout (where I was exposed to a
wide variety of A/V systems). Interfacing to a professor's laptop and
managing multiple-source feeds would be no problem for me.
\par \bigskip \smallskip

CU's expansion into online courses is a great way to help keep education
accessible for everybody, and I'd love to be a part of it. My creativity
and experience could be valuable to the OIT. If the position is still
available, I'd love the opportunity to chat more and see if we're a good
fit.
\par \bigskip \bigskip

Best regards,
\par \smallskip
Christine Waynick
}
\begin{document}%
%%%%%%%%%%%%%%% Title %%%%%%%%%%%%
\cawtitle
{\textcolor{\CawColorName}{Christine Waynick}}
{1718 Zeus Dr.}
{Lafayette, CO 80026}
{323-807-6153}
{chrissy.waynick@gmail.com}
%
\noindent \centerline {\begin{minipage}[t]{0.9\textwidth}{
\fontsize{13}{15.6}\selectfont
\setstretch{1.2}
\LetterContents}
\end{minipage}}
\end{document}
