\documentclass[letterpaper, 11pt]{article}
\usepackage[margin=0.6in]{geometry}

\usepackage{calc}

\usepackage{sweet_resume}

\usepackage{enumitem}
\usepackage{tabularx}

\usepackage[T1]{fontenc}
\usepackage{setspace}
\usepackage[usenames,dvipsnames]{xcolor}

\pagenumbering{gobble}

\definecolor{BrOrange}{HTML}{FF7F00}

\definecolor{MariPro}{HTML}{D43247}
\definecolor{DarkDark}{HTML}{000044}
\definecolor{NGreenB}{HTML}{666633}

\definecolor{BrBlue}{HTML}{FF7F00}

\newcommand{\CawColorName}{Black}
\newcommand{\CawColorTitle}{RoyalBlue}
\newcommand{\CawColorHeaderA}{MidnightBlue}
\newcommand{\CawColorSubHeaderA}{MidnightBlue}
\newcommand{\CawColorSubHeaderB}{Black}

\pdfinfo{
/Author (Christine Waynick)
/Title  (Resume - Christine Waynick)
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Macros %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\WorkExperienceLineOne}[2]{%
    \cawcolstring{\textcolor{\CawColorSubHeaderA}{\textbf{#1}}}%
    {\textcolor{\CawColorSubHeaderB}{\textbf{#2}}}%
}

\newcommand{\WorkExperienceLineTwo}[2]{%
    \cawcolstring{\small\textit{#1}}{\small\textit{#2}}%
}

\newcommand{\WorkExperienceMidBreak}{%
    \par \smallskip \smallskip%
}

\newcommand{\WorkExperienceEndBreak}{%
    \par\bigskip%
}

\newcommand{\makeheader}[1]{%
\begingroup%
    \noindent%
    \textcolor{\CawColorHeaderA}{\Large \textbf{\textsc{#1\\}}}%
    \hfill%
\endgroup%
\hfill%
}
%

%%%%%%%%%%%%%%%%%%%%%%%%% Work Experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\workKarlStorz}{%
	\WorkExperienceLineOne {Karl Storz Imaging} {Goleta, CA}
	\WorkExperienceLineTwo {FPGA Engineer III} {2013-Present}
	\WorkExperienceMidBreak

    Lead FPGA engineer on commercially-available medical video systems.
    teams to develop successful commercial products. Designed 3D, 2k and 4k
    video systems operating at NTSC and PAL frame rates.
    \WorkExperienceMidBreak
    
    Designed and implemented camera firmware for Xilinx FPGAs in Vivado and
    communication, and DVI interfaces. Wrote C applications to run on
    FPGA-hosted microcontrollers. Mentored junior engineers.
	\WorkExperienceEndBreak%
}

\newcommand{\workLthree}{%
	\WorkExperienceLineOne {L-3 Ocean Systems} {Goleta, CA}
	\WorkExperienceLineTwo {Electrical Engineer II} {2011-2013}
	\WorkExperienceLineTwo {Electrical Engineer I} {2007-2011}
	\WorkExperienceLineTwo {Electrical Engineering Intern} {2007}
	\WorkExperienceMidBreak
    \$70M coastal observatory contract with the National Science Foundation and
    the University of Washington.
    \WorkExperienceMidBreak

    underwater communication/surveillance systems. Interfaced with production and
    test engineers to oversee manufacturing runs.
	\WorkExperienceEndBreak%
}

\newcommand{\workMotionEng}{%
	\WorkExperienceLineOne {Motion Engineering, Inc} {Goleta, CA}
	\WorkExperienceLineTwo {Engineering Intern} {2006-2007}
	\WorkExperienceMidBreak
    Engineering intern. Worked with high-performance motion controllers used in
    issues and suggest workarounds for unavailable parts. Interacted directly
    with global contractors. Auctioned and sold test equipment.
	\WorkExperienceEndBreak%
}

\newcommand{\workUCSBLifesci}{%
	\WorkExperienceLineOne {UCSB Life Sciences Department} {Goleta, CA}
	\WorkExperienceLineTwo {IT Helpdesk} {2004-2006}
	\WorkExperienceMidBreak
    Provided support for 800+ faculty, staff and graduate students in two
    academic departments and two interdisciplinary graduate programs.
    Responsible for basic and advanced troubleshooting to diagnose and
    resolve both hardware and software problems. Configured and maintained
    OS X, Linux, Windows, and FreeBSD computers.
	\WorkExperienceEndBreak%
}

\newcommand{\EducationUCSB}{%
    \WorkExperienceLineOne{Brooks Institute} {Ventura, CA}
    \WorkExperienceLineTwo{B.F.A.in Video and Film Production} {2007}
	\WorkExperienceMidBreak
    Elective coursework focused on embedded systems, DSP, and technical writing.
    Active in student chapter of IEEE. Senior project on vehicular 360-degree
    FOV camera systems.
	\WorkExperienceEndBreak%
}

\hyphenation{Micro-blaze} 

\begin{document}%
%%%%%%%%%%%%%%% Title %%%%%%%%%%%%
\cawtitle
{\textcolor{\CawColorName}{Christine Waynick}}
{1718 Zeus Dr.}
{Lafayette, CO 80026}
{323-807-6153}
{chrissy.waynick@gmail.com}
%
\begin{center}\par\smallskip
\textcolor{\CawColorTitle}{\Large \textbf{\textsc{Digital Video Specialist}}}\par
\large \textbf{{Videography, Camera Operations, Production/Post-Production}}\par
\smallskip
\noindent \begin{minipage}[t]{0.75\textwidth}%
\begin{sloppypar}
Dynamic videographer with seven years experience in video production and
post-production. Skilled with cameras, lighting, equipment maintenance, and editing.
\end{sloppypar}
\end{minipage}
\end{center}
\par \smallskip \smallskip
%%%%%%%%%%%%% Column 1%%%%%%%%%%%%%%%
%
%    horizontal: leftmargin, rightmargin, itemindent, listparindent, labelwidth, labelsep
%    vertical: topsep, partopsep, parsep, itemsep
%
\newcommand{\MyColumnOne}{%
    \setitemize[0]{leftmargin=*, parsep=0pt, itemsep=0pt, topsep=0pt, partopsep=0pt}%
    \noindent \begin{minipage}[t]{0.45\textwidth}%
	\WorkExperienceMidBreak
	\WorkExperienceMidBreak
	\par \smallskip \begin{spacing}{0.95}%

    \begin{flushleft} %
    \makeheader{Live Production} \par%
    \begin{itemize}%
        \item Professional Staging and Lighting
        \item Shot Selection and Scene Design
        \item Camera and Microphone Operation
        \item Equipment Maintenance
    \end{itemize}%
	\WorkExperienceMidBreak
	\WorkExperienceMidBreak
	\WorkExperienceMidBreak
	\makeheader{Editing and Post-Production} \par%
    \begin{itemize}%
        \item Editing for Broadcast and Online Publication
        \item Sound and Color Correction
        \item Footage Logging and Archiving
        \item Coordination with Production Teams
	\end{itemize}%
	\WorkExperienceMidBreak
	\WorkExperienceMidBreak
	\WorkExperienceMidBreak
	\makeheader{Software Skills} \par%
    %    
    \WorkExperienceLineOne{Post-Production Software}{}
	\WorkExperienceMidBreak
    \begin{itemize}%	
		\item Adobe Premiere
		\item Avid Media Composer
		\item Final Cut Pro
		\item Adobe After Effects
	\end{itemize}%
    %
	\WorkExperienceMidBreak
    \WorkExperienceLineOne{General Computing}{}
	\WorkExperienceMidBreak
    \begin{itemize}%
	    \item Adobe Photoshop and Lightroom\\
	    \item Adobe Illustrator\\
	    \item OS X and Microsoft Windows\\
	    \item Microsoft Word, Excel, and Powerpoint\\
	    \item Google Docs and Google Calendar\\
	\end{itemize}%
	%
	\WorkExperienceMidBreak
	\WorkExperienceMidBreak
	\WorkExperienceMidBreak
	\makeheader{Education} \par%
	\WorkExperienceMidBreak
    \EducationUCSB

\end{flushleft}%
\end{spacing} \end{minipage}%
}
%
%%%%%%%%%%%%% Column 2%%%%%%%%%%%%%%%
%    \setitemize[0]{leftmargin=*, parsep=0pt, itemsep=0pt, topsep=0pt, partopsep=0pt}%
%    \noindent \begin{minipage}[t]{0.45\textwidth}%

\newcommand{\MyColumnTwo}{%
    \setitemize[0]{leftmargin=*, parsep=0pt, itemsep=0pt, topsep=0pt, partopsep=0pt}%
    \noindent \begin{minipage}[t]{0.45\textwidth}%
	\WorkExperienceMidBreak
	\WorkExperienceMidBreak
	\par \smallskip \begin{spacing}{0.95}%

    \begin{flushleft} %
    \makeheader{Work Experience} \par%
        \workKarlStorz
        \workLthree
        %\workMotionEng
        %\workUCSBLifesci
	
	\makeheader{Volunteer} \par%
   	\WorkExperienceLineOne{FIRST Robotics}{Goleta, CA}
   	\WorkExperienceLineTwo{Team 1717 Engineering Mentor}{2013-2015}
   	\WorkExperienceMidBreak
    Electrical engineering mentor for high-school student robotics team.
\end{flushleft}%
\end{spacing} \end{minipage}%
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%\cawtwocols
%\begin{center}$\bullet$\end{center}\par

\noindent\begin{tabularx}{\textwidth}{@{}X|X@{}} 
\hline
{\MyColumnOne\hfill} & {\hfill\MyColumnTwo}
\end{tabularx}
\end{document}
